---
title: "One-way plot"
---
  
Inputs:
  dataset - the dataset you would like to explore
  x - the variable you would like to plot on x-axis
  y - the variable you would like to plot on y-axis in form of line plot, e.g. target
  weight - the exposure variable fits into the bar plot, if none entered, default to 1
  
Returnn:
  1. A summarized data frame contains Factor, SumWeight, SumActual and AverageActual.
  2. One-way plot of the variable. 

```{r}
# Required packages
library(ggplot2)
library(data.table)
```

## Main Function

```{r}
onewayplot <- function(dataset, x, y, weight=NULL)
{
  Weight = ifelse(is.null(weight), 1, dataset[,weight])
  modeldata <- data.frame(Weight = Weight,
                          Actual = dataset[ ,y],
                          Factor = as.factor(dataset[ ,x]))
    
  dframe <- as.data.frame(data.table(modeldata)[ ,.(SumWeight = sum(Weight),
                                                    SumActual = sum(Actual),
                                                    AverageActual = sum(Actual)/sum(Weight)),
                                                    by = Factor])
    
  dframe <- dframe[order(dframe$Factor), ]
  dframe.melt <- melt(dframe [, c(1, 4)], id = c("Factor"))
  weight_max  <- max(dframe$SumWeight)
  resp_max    <- max(dframe.melt$value)
    
  plot1 <- ggplot(dframe, aes(x=Factor, y=SumWeight, group = 1)) +
             geom_bar(stat = "identity", aes(x = Factor, y = SumWeight*0.5*(resp_max)/(weight_max)),
                                             col = "black", fill = "#9EB9D4") +
             geom_line(data=dframe.melt, aes(x = Factor, y = value, color = variable, group = variable)) +
             scale_colour_manual(values = c("red")) +
             theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
             labs(title = paste("Oneway","-",x), x = "Values", y = "Target" )
    
  return(list(dframe=dframe, plot_table = plot1))
}
```

## Example

```{r}
# Borrowing an insurance dataset from cplm package
library(cplm)

dataset <- cplm::AutoClaim
dataset$claim = as.numeric(dataset$CLM_FLAG)-1
```

```{r}
onewayplot(dataset, "AGE", "claim")
onewayplot(dataset, "CAR_TYPE", "claim")
```
